---
title: "Preparing data: add feature win percent last match before"
---
 [1] "id"                               "date_match"                      
 [3] "season"                           "away_team_api_id"                
 [5] "home_team_api_id"                 "away_team_goal"                  
 [7] "home_team_goal"                   "H_overall_rating"                
 [9] "A_overall_rating"                 "H_potential"                     
[11] "A_potential"                      "H_buildUpPlaySpeed"              
[13] "H_buildUpPlaySpeedClass"          "H_buildUpPlayDribblingClass"     
[15] "H_buildUpPlayPassing"             "H_buildUpPlayPassingClass"       
[17] "H_buildUpPlayPositioningClass"    "H_chanceCreationPassing"         
[19] "H_chanceCreationPassingClass"     "H_chanceCreationCrossing"        
[21] "H_chanceCreationCrossingClass"    "H_chanceCreationShooting"        
[23] "H_chanceCreationShootingClass"    "H_chanceCreationPositioningClass"
[25] "H_defencePressure"                "H_defencePressureClass"          
[27] "H_defenceAggression"              "H_defenceAggressionClass"        
[29] "H_defenceTeamWidth"               "H_defenceTeamWidthClass"         
[31] "A_buildUpPlaySpeed"               "A_buildUpPlaySpeedClass"         
[33] "A_buildUpPlayDribblingClass"      "A_buildUpPlayPassing"            
[35] "A_buildUpPlayPassingClass"        "A_buildUpPlayPositioningClass"   
[37] "A_chanceCreationPassing"          "A_chanceCreationPassingClass"    
[39] "A_chanceCreationCrossing"         "A_chanceCreationCrossingClass"   
[41] "A_chanceCreationShooting"         "A_chanceCreationShootingClass"   
[43] "A_chanceCreationPositioningClass" "A_defencePressure"               
[45] "A_defencePressureClass"           "A_defenceAggression"             
[47] "A_defenceAggressionClass"         "A_defenceTeamWidth"              
[49] "A_defenceTeamWidthClass"          "result"

```{r}
dataset <- read.csv(file.path('datasets', 'data_preparing.csv'))
```

```{r}
#data <- subset(dataset, select = c(home_team_api_id, away_team_api_id, home_team_goal, away_team_goal, result))
data <- dataset
head(data)
```

###############################################################################################################

**FACTOR MATCH A vs B **

```{r}
a <- which(data$home_team_api_id == 10261)
b <- which(data$away_team_api_id == 8455)
f_ab <- factor(a,b)[which(!is.na(factor(a,b)))]
f_ab <- as.numeric(as.character(f_ab))
rm(a, b)
data[f_ab, ]
```

**FACTOR MATCH A2 vs B2 **

```{r}
a2 <- which(data$home_team_api_id == 8455)
b2 <- which(data$away_team_api_id == 10261)
f2_ab <- factor(a2,b2)[which(!is.na(factor(a2,b2)))]
f2_ab <- as.numeric(as.character(f2_ab))
rm(a2, b2)
data[f2_ab, ]
```

**INDEX MATCH A vs B and A2 vs B2**

```{r}
temp <- c(21, 300, 892, 1087, 1304, 1439, 1576, 1760, 2043)
temp2 <- sort(c(f_ab, f2_ab))
```


###############################################################################################################

*Adding new column*
  n                    : number of match time A vs B
  sum_goals home away  : h_sum_goals, a_sum_goals
  n win, draw          : h_nwin, a_nwin, ha_ndraw
  

```{r}
data$n <- 1
data$h_sum_goals <- 0
data$a_sum_goals <- 0
data$h_nwin <- 0
data$a_nwin <- 0
data$ha_ndraw <- 0
data$h_sum_goals[1] <- data$home_team_goal[1]
data$a_sum_goals[1] <- data$away_team_goal[1]
```


```{r}
 addNGoals <- function(data){
   for(nr in 2:nrow(data)){
     h <- data$home_team_api_id[nr]
     a <- data$away_team_api_id[nr]
     n <- 0; hg <- 0; ag <- 0; 
     hwin <- 0; awin <-0; hadraw <- 0;
     for(renum in nr:2){
       renum <- renum - 1
       if(h == data$home_team_api_id[renum] || h == data$away_team_api_id[renum]){
         if(a == data$home_team_api_id[renum] || a == data$away_team_api_id[renum]){
           n <- data$n[renum]
           if(h == data$home_team_api_id[renum]) { 
             hg <- data$h_sum_goals[renum]
             ag <- data$a_sum_goals[renum]
             hwin <- data$h_nwin[renum]
             awin <- data$a_nwin[renum]
            }
           else {  
             hg <- data$a_sum_goals[renum]; 
             ag <- data$h_sum_goals[renum]
             hwin <- data$a_nwin[renum]
             awin <- data$h_nwin[renum]
           }
           hadraw <- data$ha_ndraw[renum];
           break
         }
       }
     }
     data$n[nr] <- n + 1
     data$h_sum_goals[nr] <- data$home_team_goal[nr] + hg
     data$a_sum_goals[nr] <- data$away_team_goal[nr] + ag
     data$h_nwin[nr] <- hwin
     data$a_nwin[nr] <- awin
     data$ha_ndraw[nr] <- hadraw
     if( data$home_team_goal[nr] > data$away_team_goal[nr]) { data$h_nwin[nr] <- data$h_nwin[nr] + 1 }
     else if( data$home_team_goal[nr] < data$away_team_goal[nr] ) { data$a_nwin[nr] <- data$a_nwin[nr] + 1}
     else { data$ha_ndraw[nr] <- data$ha_ndraw[nr] + 1}
   }
   return(data)
 }
data_ngoals <- addNGoals(data)
data_ngoals[temp, ]
```


###############################################################################################################

*Adding new column*
  percent_win home, away, draw: h_percent_win, a_percent_win, percent_draw 

#percent
```{r}
data_ngoals_percent <- data_ngoals
data_ngoals_percent$h_percent_win <- 0.0
data_ngoals_percent$a_percent_win <- 0.0
data_ngoals_percent$percent_draw <- 0.0
```

```{r}
addPercent <- function(data){
  data$h_percent_win[1] <- 33.333
  data$a_percent_win[1] <- 33.333
  data$percent_draw[1] <- 33.333
  n_max_loop <- nrow(data) - 1
  for(nr in 2:n_max_loop){
    #data$h_percent_win[nr] <- (data$h_nwin[nr-1]/data$n[nr-1])*100
    #data$a_percent_win[nr] <- (data$a_nwin[nr-1]/data$n[nr-1])*100
    #data$percent_draw[nr] <- (data$ha_ndraw[nr-1]/data$n[nr-1])*100
    h <- data$home_team_api_id[nr]
    a <- data$away_team_api_id[nr]
    last_h_nwin <- 0
    last_a_nwin <- 0
    last_ndraw <- 0
    last_n <- 0
    for(renum in nr:2){
      renum <- renum - 1
       if(h == data$home_team_api_id[renum] || h == data$away_team_api_id[renum]){
         if(a == data$home_team_api_id[renum] || a == data$away_team_api_id[renum]){
           if(h == data$home_team_api_id[renum]) { 
             last_h_nwin <- data$h_nwin[renum]
             last_a_nwin <- data$a_nwin[renum]
            }
           else {  
             last_h_nwin <- data$a_nwin[renum]
             last_a_nwin <- data$h_nwin[renum]
           }
           last_n <- data$n[renum]
           last_ndraw <- data$ha_ndraw[renum]
           break
         }
       }
    }
    if(data$n[nr] == 1){
      data$h_percent_win[nr] <- 33.333
      data$a_percent_win[nr] <- 33.333
      data$percent_draw[nr] <- 33.333
    }else {
    data$h_percent_win[nr] <- (last_h_nwin/last_n)*100
    data$a_percent_win[nr] <- (last_a_nwin/last_n)*100
    data$percent_draw[nr] <- (last_ndraw/last_n)*100
    }
  }
  return(data)
}
data_ngoals_percent <- addPercent(data_ngoals_percent)
data_ngoals_percent[temp, ]
data_ngoals_percent[temp2, ]
```


*VIEW FOR TESTING*

```{r}
subset(data_ngoals_percent[temp2, ], select = c(away_team_api_id, home_team_api_id, result, n, h_nwin, a_nwin, ha_ndraw, h_percent_win, a_percent_win, percent_draw))
```

*Write file*

```{r}
write.csv(data_ngoals_percent, 'data_ngoals_percent.csv')
```


